Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-08-30 manuscript/manuscript.tex
PR review requested changes cw, beh

\subsection{Markov models of large systems}
For modeling large systems, challenges arise that are mostly system dependent. 
One of them is that finding a state space discretization using e.g. $k$-means becomes difficult in very high dimensional spaces. 
It is thus important to choose a feature space and coordinate transform that yield a low dimensional representation of the slow processes.
Hidden Markov models might further help to overcome poor discretization to a certain extend.

In addition, the slowest process in a system as identified by a Markov model might not be the one a modeler is interested in. 
For instance, there might be a side chain flip that only occured once in a data set but has no biological relevance. 
This problem can often be mitigated by choosing a more specific set of features.

We explain how to deal with the technical challenges such as limited memory in the tutorials. 
More details on how to model complex systems with the techniques presented here are described by e.g. ~\cite{plattner_protein_2015,plattner_complete_2017}.

>>>>

\subsection{Markov models of large systems}
For modeling large systems, challenges may arise that are mostly system dependent. 
For example, one of them is that finding a state space discretization using e.g.~ $k$-means becomes difficult in very high dimensional spaces. 
It is thus important to choose a feature space and coordinate transformion that yield a low dimensional representation of the slow processes.
Hidden Markov models might further help to overcome poor discretization to a certain extend \cite{noe-proj-hid-msm}.

In addition, the slowest process in a system as identified by a Markov model might not be the one a modeler is interested in. 
For instance, there might be a side chain flip that only occurred once in a data set but has no biological relevance. 
This problem can often be mitigated by choosing a more specific set of features.

Further, large systems come with technical challenges such as huge memory requirements.
We explain how to deal with those in the tutorials. 
More details on how to model complex systems with the techniques presented here are described by e.g. ~\cite{plattner_protein_2015,plattner_complete_2017}.
